BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-27 tex/3-algorithms.tex
Variations done.

% algorithm, inputs/output
Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for blog post contents. It takes as input a set of pairs of HTML pages and target contents, and returns an extraction rule. This rule will be such that when applied input pages, the extracted texts are close to the corresponding target contents. \comment{this last sentence might not be very clear (?), but this is very important.}%

@@

% linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rule prevents an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information of where the string could be spitted into substring with already computed bigrams is not accessible, and the bigrams of the page has to be computed by linearly traversing the full string. To overcome this limitation and implement an effective $memoization$ \comment{without R!}over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from it's children bigrams, effectively avoiding serialization of HTML subtrees.

@@

% Dates, authors
Dates are affected by the same duplication issue, as well as inconsistence of format between web feeds and web pages. Our solution to build date extraction rules extends what we presented before for authors by using multiple \emph{target} strings. For instance, if the feed indicates that a post was published on \stringliteral{2013-12-09}, our algorithm will search for a rule to extract one of \stringliteral{}, \stringliteral{}, \stringliteral{} and so on. We use a list of \TODO{0} target date formats that was empirically built during our experiments. While this list is certainly not exhaustive, our approach using string similarity on multiple target is robust to format changes. We did not took the time to support dates in multiple languages but it would be a straightforward modification.

% Comments
Comments are usually available is separated web feeds, organized by blog post. Similarity to blog feeds, comment feeds have a limited number en entries, and in case of overflow content has to be extracted from the post web page.

>>>>

% algorithm, inputs/output
Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for blog post contents. It takes as input a set of pairs of HTML pages and target contents, and returns an extraction rule. This rule will be such that when applied input pages, the extracted texts are close to the corresponding target contents. \comment{this last sentence might not be clear (?), this is quite important.}%

@@

% Linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rule prevents an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information of where the string could be spitted into substring with already computed bigrams is not accessible, and the bigrams of the page has to be computed by linearly traversing the full string. To overcome this limitation and implement $memoization$ \comment{without R!}over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from children bigrams. This way we avoid serializing HTML subtrees at each bigrams computation and have a guaranty that each character of the HTML page will be read at most once during bigrams computations. Thus, the cumlated time needed to compute bigrams of \emph{node.text} is linear.

% End of proof
To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all its inner loop computations other than bigrams of \emph{node.text} can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iterations is one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams lenght computation. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operation can be done in constant time.

@@

% Dates, authors
Dates are affected by the same duplication issue, as well as inconsistence of format between web feeds and web pages. Our solution to build date extraction rules extends what we presented before for authors by using multiple \emph{target} strings. For instance, if the feed indicates that a post was published on
\stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule to extract one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. We use a list of \TODO{none so far :(} target date formats that was empirically built during our experiments. While this list is certainly not exhaustive, our approach using string similarity on multiple target is robust to format changes. We did not took the time to support dates in multiple languages but it would be a straightforward modification.

% Comments
Comments are usually available in a separated web feeds, organized by blog post. Similarity to blog feeds, comment feeds have a limited number en entries, and in case of overflow data has to be extracted from the post web page. To do so we use algorithm \ref{extractionAlgo} with the following modifications:
\begin{enumerate}
  \item\label{lessthanfeedMod} Rules that return less HTML nodes than the number of comments on the feed are filtered out.
  \item\label{assignmentMod} The score of a rule is the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
\end{enumerate}
Our crawler executes this algorithm on each page with comment overflow, and thus supports blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down modification \ref{lessthanfeedMod} by fixing the target number of comments.

### 2013-11-27 tex/5-evaluation.tex
Variations done.

\subsection{Content extraction}
Compare:
\begin{itemize}
  \item Our solution
  \item Boilerpipe https://github.com/misja/python-boilerpipe
  \item Goose https://github.com/grangier/python-goose
  \item Readability https://github.com/buriy/python-readability
\end{itemize}
On:
\begin{enumerate}
  \item Running time
  \begin{itemize}
    \item Plot duration as a function of the page length
    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
  \end{itemize}
  \item Quality of output compared:
  \begin{itemize}
    \item Chart of success pourcentages
  \end{itemize}
\end{enumerate}

\subsection{JavaScript rendering}
Compare:
\begin{itemize}
  \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/\\creating-a-snapshot-of-a-blog-post-using-wget/
  \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
  \item Selenium + full browser
  \item probably others
\end{itemize}
On:
\begin{itemize}
  \item Table comparing functionalities of each solution
  \item Histogram of redering time per browser\\(phantomjs/chrome/firefox)
\end{itemize}

@@

>>>>

\subsection{Content extraction}
Compare:
\begin{itemize}
  \item Our solution
  \item Boilerpipe https://github.com/misja/python-boilerpipe
  \item Goose https://github.com/grangier/python-goose
  \item Readability https://github.com/buriy/python-readability
\end{itemize}
On:
\begin{enumerate}
  \item Quality of output compared, Chart of success pourcentages
  \item Running time, Plot duration as a function of the number or pages (our should only take time to build the rules)
\end{enumerate}

\subsection{JavaScript rendering}
Compare:
\begin{itemize}
  \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/\\creating-a-snapshot-of-a-blog-post-using-wget/
  \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
  \item Selenium + full browser
  \item probably others
\end{itemize}
On:
\begin{itemize}
  \item Table comparing functionalities of each solution
  \item Histogram of redering time per browser\\(phantomjs/chrome/firefox?)
\end{itemize}

@@

\begin{figure}[htbp]
  \centering
  \begin{gnuplot}[terminal=epslatex,terminaloptions=color]
    plot [0:2*pi] sin(x) title 'Sine', cos(x) title 'Cosine'
  \end{gnuplot}
\end{figure}
